---
title: "Mini-Challenge EDA - Krankenkassenprämien von Privatkunden"
output: html_notebook
---

Load Packages

```{r}
library(tidyverse)
library(moments)
library(skimr)
```

Import the data

```{r}
data = read.csv('./data/versicherung_krankenkassenpraemie.csv')
```

Overview of the data

```{r}
str(data)
```

```{r}
glimpse(data)
```

```{r}
summary(data)
```

```{r}
skim(data)
```

get a closer look at age distribution

```{r}
ggplot(data, aes(age)) +
  geom_density()
```

5 Point Summary for age

```{r}
ggplot(data, aes("", age)) +
  geom_boxplot() +
  geom_point(position="jitter",alpha=0.2)
```

There seems to be an even distribution around all age groups

Check for connections between different variables

```{r}
ggplot(data, aes(age,color=smoker)) +
  geom_density()
```


```{r}
ggplot(data, aes(region,fill=smoker)) +
  geom_bar()
```


Check if there is a connection between age and charges

```{r}
ggplot(data, aes(age,charges)) +
  geom_point()
```

There is indeed. In general charges seem to be higher, with higher age. 
There seems to also be a split of the charges in three groups. Lets see why that is.

```{r}
ggplot(data, aes(age,charges,color=region)) +
  geom_point()
```

Its definitely not regions.

```{r}
ggplot(data, aes(age,charges,color=smoker)) +
  geom_point(position="jitter")
```

Not really suprisingly there is a correlation between charges and smokers. where in general, non smokers pay much less.

```{r}
ggplot(data, aes(charges,bmi)) +
  geom_smooth()
```

I need to have a closer look at the bmi values

```{r}
ggplot(data, aes(bmi)) +
  geom_histogram()
```

```{r}
summary(data$bmi)
sd(data$bmi)
moments::skewness(data$bmi)
moments::kurtosis(data$bmi)
```

```{r}
data <- data %>% mutate(bmi_gr = as.factor(case_when( bmi < 10.0 ~ "nicht überlebensfähig",
                             bmi < 18.5 ~ "untergewichtig",
                             bmi < 25.0 ~ "normalgewichtig",
                             bmi < 30.0 ~ "übergewichtig",
                             bmi >=30.0 ~ "behandlungsbedürftig",
                             TRUE ~ "unbekannt")))
```



```{r}
str(data)
```



